A data-intensive assessment of the species-abundance distribution.

### 2015-03-19 defense_pres.tex
Adds data, fiddles with formatting, starts analysis?

\section{Species abundance distribution}
\begin{frame}[t]{}
\frametitle{Commonness \& rarity}
~\\
\begin{large}
The species abundance distribution:
\end{large}
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\item One of the most fundamental and ubiquitous patterns in ecology.
\item Exhibits a hollow curve distribution.
\begin{itemize}
\item Many rare species.
\item Few common species.
~\\
\end{itemize}
\item Many forms of the species abundance distribution (SAD).
\end{itemize}
\end{frame}

\section{Species abundance distribution comparisons}
\subsection{Analysis}
\subsection{Results}
\begin{frame}{}
\frametitle{SAD Comparisons}
\includegraphics[scale=.5]{./sad-data/chapter1/AICc_weights.png}
\end{frame}

>>>>

\section{The species abundance distribution}
\subsection{Pattern description}
\begin{frame}[t]{}
\frametitle{Commonness \& rarity}
~\\
\begin{large}
The species abundance distribution:
\end{large}
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\item One of the most fundamental and ubiquitous patterns in ecology.
\item Exhibits a hollow curve distribution.
\begin{itemize}
\item Many rare species.
\item Few common species.
~\\
\end{itemize}
\item Many forms of the species abundance distribution (SAD).
\end{itemize}
\end{frame}

\subsection{Forms of the distribution}
\begin{frame}
\frametitle{Forms of the SAD}
\begin{large}
Model classes:
\end{large}
\begin{itemize}
\item Purely statistical
\item Branching process
\item Population dynamics
\item Niche partitioning
\item Maximum entropy
\item Feasible set/combinatorics
\end{itemize}
\end{frame}

\section{Species abundance distribution comparisons}
\begin{frame}
\frametitle{SAD Comparisons}
\begin{large}
Most comparisons of the different models:
\end{large}
\begin{itemize}
\item Use only a small subset of available models (typically two).
\item Focus on a single ecosystem or taxonomic group
\item Fail to use the most appropriate statistical methods. 
\end{itemize}
\end{frame}

\subsection{Analysis}
\begin{frame}[shrink=10]
\frametitle{SAD Comparisons}
~\\
~\\
Selected five models from four classes for comparison.
\begin{table}
\begin{tabular}{l|l}
 Model class & Form of the distribution\\ 
\hline
 Purely statistical & Logseries, Poisson lognormal\\
 Branching process & Zipf \\
 Population dynamics & Negative binomial\\
 Niche partitioning & Geometric \\
\end{tabular}
~\\
~\\
~\\
~\\
\caption{After B.J. McGill et al. 2007. Species abundance distributions: moving beyond single prediction theories to integration within an ecological framework. Ecology letters 10: 995-1015.}
\end{table}
\end{frame}

\begin{frame}[shrink=35]
\frametitle{SAD Comparisons}
\begin{center}
\begin{table}
\begin{tabular}{l|c|l|r}
 Dataset &Dataset code &Availability &Total sites\\
\hline
 Breeding Bird Survey &BBS &Public &2769\\
 Christmas Bird Count &CBC &Private &1999\\
 Gentry's Forest Transects &Gentry &Public &10355\\
 Forest Inventory Analysis &FIA	 &Public &220\\
 Mammal Community Database &MCDB &Public &103\\
 N. American Butterfly Count &NABA &Private &400\\
 Actinopterygii, this dissertation	 &Actinopterygii &Public &161\\
 Reptilia, this dissertation &Reptilia &Public &138\\
 Amphibia, this dissertation &Amphibia &Public &43\\
 Coleoptera, this dissertation &Coleoptera &Public &5\\
 Arachnida, this dissertation &Arachnida &Public &25\\
\end{tabular}
\caption{Datasets used for species-abundance distribution comparisons. Datasets marked as Private were obtained through data requests to the providers resulting in Memorandums of Understanding governing data use.}
\end{table}
\end{center}
\end{frame}

\subsection{Results}
\begin{frame}{}
\frametitle{SAD Comparisons}
\includegraphics[scale=.5]{./sad-data/chapter1/AICc_weights.png}
\end{frame}
